---
title: "Replication of Cheynel and Liu-Watts (2020)"
author: "Shunsuke Matsuno"
date: "2020/7/28"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r settings, echo=FALSE}
### Setting the global code chunk options ###
# Args
#   comment='': won't append any string to the start of each line of results
#   fig.align='center': align figures to the center of document
knitr::opts_chunk$set(comment="", fig.align="center", warning = FALSE)
```

# Description
- "A Simple Structural estimator of Disclosure Costs" by Cheynel and Liu-Watts, 2020, RAST.
- In this note we replicate Section 2.5 of the original paper.
- In addition, we check the behavior of the proposed estimator with several underlying distributions of firm values.
- All the original functions can be found [here](https://github.com/ShunsukeMatsuno/DisclosureCost).

# Required libraries
```{r, message=FALSE}
easypackages::libraries('tidyverse', 'ggplot2', 'patchwork', 'CheynelLiuWatts')
```


# Simulation
- There are $N=10,000$ firms and each firm has $T=40$ periods.
- Private signal $x$ is drawn from standard normal distribution.
    - Note that $x$ is actually the manager's posterior expectation about future earnings. However, we can effectively regard that manager observes random $x$ and investors form belief about $x$.
- The cost of disclosure $c$ is randomly assigned to firms, where $c \in \{ 0.4, 0.5, \dots, 2.1 \}$. 
    
```{r}
# seed
set.seed(2020)

# simulation settings
num_firms <- 10000    # 10,000 firms for each cost
time <- 40            # 40 periods for each firm
c <- seq(0.4, 2.1, by = .1)  # grid of cost
N <- num_firms * length(c)    
```

## Simulating true cost and disclosure
- Each firm has 40 periods.
- `x` is the private inforamtion about firm value, which is iid across firms and over time.
```{r}
# firm
df_firm <- tibble(
  firm = rep(1:N, each = time),
  time = rep(1:time, times = N),
  x = rnorm(N*time)
)
df_firm
```
- The cost of disclosure $c$ is assumed to vary across firms but constant over period in each firm.
```{r}
df_firm <- df_firm %>% 
  group_by(firm) %>% 
  mutate(c = sample(c, 1)) %>% 
  ungroup()
df_firm
```

- The threshold is determined by
$$
\tau - c = \mathbb{E}[x \mid x \le \tau].
$$
- To solve this equation, we write a function that computes $\mathbb{E}[x \mid x \le \tau] - (\tau - c )$, and minimize it.
- `compute_threshold.R` do this computation.
    - The following code takes a couple of minutes.
```{r}
df_firm <- df_firm %>% 
  group_by(firm) %>% 
  mutate(tau = compute_threshold(x, c)) %>% 
  ungroup()
df_firm  
```

- If $x>=\tau$, then firm's disclose their $x$, and if not, they do not disclose.
```{r tau}
df_firm <- df_firm %>% 
  mutate(disclosure = if_else(x >= tau, x, NA_real_))
df_firm
```

- Finally, for the purpose of estimation, each firm must have at least one period of disclosure and one period of non-disclosure.
    - Firms that do not satisfy this criterion ( (not) disclosing in all periods) are dropped from sample.
```{r}
df_firm <- df_firm %>% 
  group_by(firm) %>% 
  mutate(remain_firm = 
           if_else(
             sum(!is.na(disclosure)) == 0 | sum(is.na(disclosure)) == 0,
             FALSE,
             TRUE)) %>% 
  ungroup() %>% 
  filter(remain_firm) %>% 
  select(-remain_firm)     # this variable is no longer needed
``` 
    
## Estimation
- Using the simulated data, we estimate the cost of disclosure by the following procedure:
1. Estimate $p$, $\tau$, $m := \mathbb{E}[x\mid x>\tau]$.
    - $\hat{p} = \text{sample disclosure frequency}$
    - $\hat{\tau} = \min\{\text{observed } x\}$
    - $\hat{m} = \text{average forecast surprise}$ 
2. Estiate $c$ by
$$
\begin{align*}
\hat{c}_{\textit{NP}} & =\max\left(0,\hat{\tau}+\frac{\hat{p}}{1-\hat{p}}\hat{m}\right),\\
\hat{c}_{\textit{BBT}} & =\Phi^{-1}(1-\hat{p})+\frac{\phi\left(\Phi^{-1}(1-\hat{p})\right)}{1-\hat{p}}.
\end{align*}
$$

- `estimate_c_NP.R` and `estimate_c_BBT.R` do this procedure.
```{r}
df_cost <- df_firm %>% 
  mutate(c_NP  = estimate_c_NP(.),
         c_BBT = estimate_c_BBT(.))
df_cost
```

- Since we know the true cost, we can compute bias and absolute error.
```{r}
df_cost <- df_cost %>% 
  mutate(bias_NP   = c_NP - c,
         bias_BBT  = c_BBT - c,
         error_NP  = abs(c_NP - c),
         error_BBT = abs(c_BBT - c))
```

- Plot bias and error (Fig.1 of original paper).
```{r}
# bias
df_cost_plot_bias <- df_cost %>% 
  group_by(c) %>% 
  summarise(across(bias_NP:bias_BBT, mean),
            .groups = "drop") %>% 
  pivot_longer(-c, names_to = 'type', values_to = 'bias')
  
g1 <- ggplot(df_cost_plot_bias, aes(x = c, y = bias, color = type)) +
  geom_line(aes(linetype = type), size = 1) + 
  theme_bw() +
  theme(legend.position = 'top') 

# error
df_cost_plot_error <- df_cost %>% 
  group_by(c) %>% 
  summarise(across(error_NP:error_BBT, mean),
            .groups = "drop") %>% 
  pivot_longer(-c, names_to = 'type', values_to = 'error')
  
g2 <- ggplot(df_cost_plot_error, aes(x = c, y = error, color = type)) +
  geom_line(aes(linetype = type), size = 1) +
  theme_bw() +
  theme(legend.position = 'top') 

p <- g1 + g2 + plot_layout(ncol = 1) 
plot(p)
ggsave("cost_simulated.png", p, path = "../output/figure", width = 8, height = 5)
```
## Robustness to distrbtutional assumption
- What happens if $x$ is not distributed normally? 
    - BBT estimator assumes that $x$ follows normal distribution.
    - NP estimator does not impose any distributional assumption on $x$.
- `bias_error_plot_distribution.R` plots bias and error with several distributional assumptions.
    - `dist = 1`: standard normal
    - `dist = 2`: uniform dist. over $[0,1]$
    - `dist = 3`: exponential dist. with rate $1$ 
    - `dist = 4`: t-dist. with df $5$
- As shown in the following figures, NP estimator outperforms BBT estimator only in the case of uniform distribution. 
    - The assumption of uniform distribution is often put in theoretical literature, so this characteristics is important.
    - However, the robustness of BBT estimator is surprising.
    - For example, the exponential distribution with rate $1$ is quite skewed compared to standard normal, while BBT estimator which assumes normality offers good estimates.
    
```{r,message=FALSE}
library(doParallel)
cl <- makePSOCKcluster(parallel::detectCores(logical = FALSE))
doParallel::registerDoParallel(cl)

obj <- numeric(4)

obj <- foreach (i = 1:4,
        .packages = c('dplyr', 'ggplot2', 'patchwork', 'tidyr', 'CheynelLiuWatts')) %dopar% {
  obj[i] <- bias_error_plot_distribution(dist = i, 
                                         num_firms = num_firms, 
                                         time = time)
}

stopCluster(cl)

obj
```

